Predicting the Popularity of Children’s Books Considering Reader’s Rating, Physical Attributes and Trend

### 2024-12-02 paper/paper.qmd
fixed telegraphing paragraph

The remainder of this paper is structured as follows. Section [@sec-data] describes the dataset used in the study, including details on the simulated data generation process, the attributes of children’s books considered, and the assumptions underlying the variables. Section [@sec-model] outlines the analytical techniques employed, including statistical models, as well as the rationale for their selection. Section [@sec-results] presents the findings of the analysis, highlighting the relationships between book attributes and popularity and providing interpretations of key predictors. Section [@sec-discussion] discusses the implications of the results for publishers, including actionable insights and strategies for leveraging the findings to maximize reader engagement.

>>>>

The remainder of this paper is structured as follows. [@sec-data] describes the dataset used in the study, including details on the simulated data generation process, the attributes of children’s books considered, and the assumptions underlying the variables. [@sec-model] outlines the analytical techniques employed, including statistical models, as well as the rationale for their selection. [@sec-results] presents the findings of the analysis, highlighting the relationships between book attributes and popularity and providing interpretations of key predictors. [@sec-discussion] discusses the implications of the results for publishers, including actionable insights and strategies for leveraging the findings to maximize reader engagement.
